Counting infinitely by Oritatami co-transcriptional folding

### 2019-06-17 paper.tex
writing general idea

>>>>

\section{Folding an infinite binary counter}

\subsection{General idea}
Basically, an folding process of counter is the same way as Geary et al \cite{counter2016}.
The construction proceeds in zig-zags.
Each pass is 3-rows thick and folds each part of the bead into a glider or turn module.
Each pass extends to straight while folding into glider and folds its last module folds into turn module and starts next pass.
The zig pass, folding from right to left, counts up in the current value of the counter.
The zag pass, folding from left to right, formats and copy to downward the value which the zig pass represents.

The module is semantically divided into 4 parts, called modules:
\begin{itemize}
\item Module F (beads 1--30): the Format module
\item Module L (beads 31--66): the Left-Turn module
\item Module H (bead 67--96): the Half-Adder module
\item Module R (bead 97--132): the Right-Turn module 
\end{itemize}

\subsubsection{Encoding}
The current value of the counter is encoded in standard binary with the most significant bit to the left.
Binary is encoded into a specific folding of the module F and H.
In zig pass, folding of module H corresponds to module F in a zag pass: namely H0 for 0, and H1 for 1.
In addition, start position of modules represents the carry: carry = 0 if module H starts to fold in the top row; carry = 1 if module H start to fold from the bottom row.
On the other hand in zag pass, folding of module F corresponding to module H in a zig pass: namely F0 for 0, and F1 for 1.

\subsubsection{In the zig pass ($\leftarrow$)}
Module H read from the row above the value encoded into folding in the module F during the previous zag-phase, and fold into a shape H00, H10, H01, H11.
H$xc$ is corresponding to the case where $x$ is the bit read in the row above and $c$ is the carry. 
In the zig pass module R, F, and L just propagate the carry value to the next.

When the zig pass reaches the left most part, module L collaborates with above turn module and it is folded turn module which reverses the folding direction for next zag pass except carry = 1.
At this time, if module L has a carry, folding of module L is glider and it go straight in order to expand bit width after that next module L turns to zag pass while folding turn module.
%H -> He1

\subsubsection{In the zag pass ($\rightarrow$)}
Module F read form the row above H$xc$, and fold into a shape F0, F1.
F$y$ is corresponding to the case where $y = (x + c) mod 2$.
There are no carry propagation and the module L, H, R fold into Lbc, Hn, Rb in this pass.

When the zag pass reaches the right most part. module R collaborates with above turn module and it is folded turn module which reverses the folding direction for next zag pass.
